Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
abstract added by yny

%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

@@

%
The electrostatic
natures of lipid molecules (a hydrophobic tail and a hydrophilic head
with an electric dipole) complicate the interactions between a lipid
bilayer membrane and another bilayer
membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces,PerutkovaFrank-Bertoncelij2013_CSB} 
or a solid (such as a glass substrate
or a nano particle).  it is reported that such complicated electrostatic contribution in the adhesive interactions between two membranes can be well approximated by the 
L-J-type potential \cite{FlormannAouane2017_SciReports}, which consists of a long-range attraction component and a
short-range repulsion component~\cite{Book_IntermolecularSurfaceForces},
and the combination of the two gives rise to adhesion at the separation
distance that minimizes the interaction
potential~\cite{Book_IntermolecularSurfaceForces}. Such adhesive
potentials are essential in many biomedical, biological and biophysical
processes.  For example, vesicle adhesion is essential for membrane
fusion/fission in endocytosis and exocytosis, the transport of small
vesicles through membrane surfaces.

>>>>

The dynamic consequences of weakly adhesive vesicles under various flowing conditions are investigated numerically using a boundary integral formulation with
adaptive time-marching that facilitates efficient and accurate computations of vesicle hydrodynamics under adhesion. In a quiescent flow, a lubrication analysis illustrates the scaling in 
the draining dynamics with respect to the adhesion strength and length scale. In a microfluid trap, results from boundary integral simulations show that there exists a critical extensional flow rate above which the weak adhesive interaction is overcome by the hydrodynamic diverging stream, thus providing a simple method to measure the adhesion strength between two vesicle membranes. In a planar shear flow, numerical simulations reveal that a vesicle doublet may form as they approach each other in a planar shear flow provided that the adhesion
strength is sufficient large at a given vesicle reduced area. Once a doublet the effective shear viscosity of a dilute suspension of vesicle doublets is found 
to be a function of both reduced area and the adhesion strength.
Results from these numerical studies and analysis shed light on the hydrodynamic effects of adhesive interactions between vesicles in a viscous fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

@@

%
The electrostatic
natures of lipid molecules (a hydrophobic tail and a hydrophilic head
with an electric dipole) complicate the interactions between a lipid
bilayer membrane and another bilayer
membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces,PerutkovaFrank-Bertoncelij2013_CSB} 
or a solid (such as a glass substrate
or a nano particle).  It is reported that such complicated electrostatic contribution in the adhesive interactions between two membranes can be well approximated by the 
L-J-type potential \cite{FlormannAouane2017_SciReports}, which consists of a long-range attraction component and a
short-range repulsion component~\cite{Book_IntermolecularSurfaceForces},
and the combination of the two gives rise to adhesion at the separation
distance that minimizes the interaction
potential~\cite{Book_IntermolecularSurfaceForces}. Such adhesive
potentials are essential in many biomedical, biological and biophysical
processes.  For example, vesicle adhesion is essential for membrane
fusion/fission in endocytosis and exocytosis, the transport of small
vesicles through membrane surfaces.
